---
title: "My Report"
author: "Esarrah Hopkins"
date: "6/24/2021"
output: html_document
bibliography: bibliography.bib
---

```{r, include=FALSE, echo = TRUE, eval = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = TRUE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE)
```

```{r, echo = FALSE}
library(dplyr)
smoker <- c(TRUE, TRUE, TRUE, TRUE,FALSE, FALSE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE, FALSE, TRUE, TRUE)
age<- c(19, 21, 22, 23, 24, 20, 21, 20, 22, 21, 19, 19, 20, 22, 19)
people <- data.frame(smoker, age)
people <- people %>% filter(age <= 34)
obs <- nrow(people)
```


# **Introduction**
## Background
### Smoking: Is it good for you?
Everyone knows smoking is bad for you.
[@Rudd2014].

### How many people smoke?
Many people smoke.

# Methods
My colleagues and I surveyed `r obs` people. The average age of participants is `r round(mean(people$age))` years. This is **very** _young_.


# **Results**
The below charts shows the age of the participants.
```{r, echo = FALSE}
library(ggplot2)
ggplot(data = people,
       aes(x = age,
           y = smoker)) +
  geom_boxplot()

```


# Conclusion
Some participants have smoked, and some have not. Yay.

# Bibliography
